Results

### 2019-09-19 analysis/03_analysis.Rmd
Updating visualizations and working on ggridges code.

# Plot marginals
if (intercept == 1) {
  draws %>% 
    mutate(
      levels = factor(i, labels = level_labels)
    ) %>%
    ggplot(aes(x = Theta, y = levels)) + 
    geom_halfeyeh(.width = .95) +
    geom_vline(xintercept = 0, color = "grey") +
    labs(y = "Attribute Levels")
}
if (intercept != 1) {
  draws %>% 
    filter(j != 1) %>% 
    mutate(
      levels = factor(i, labels = level_labels),
      covariates = factor(j, labels = covariate_labels)
    ) %>%
    ggplot(aes(x = Theta, y = covariates)) + 
    # what other geoms could we use
    # geom_ridgeline(fill="lightblue") +
    geom_density_ridges() +
    # geom_density_ridges2
    # geom_density_ridges_gradient
    # geom_halfeyeh(.width = .95) +
    geom_vline(xintercept = 0, color = "grey") +
    labs(y = "Covariates") +
    facet_wrap(~ levels, ncol = 5)
}

>>>>

# Plot marginals
if (intercept == 1) {
  draws %>% 
    mutate(
      levels = factor(i, labels = level_labels)
    ) %>%
    ggplot(aes(x = Theta, y = levels)) + 
    geom_halfeyeh(.width = .95) +
    geom_vline(xintercept = 0, color = "grey") +
    labs(y = "Attribute Levels")
}
if (intercept != 1) {
  draws %>% 
    filter(j != 1) %>% 
    mutate(
      levels = factor(i, labels = level_labels),
      covariates = factor(j, labels = covariate_labels)
    ) %>%
    ggplot(aes(x = Theta, y = covariates)) + 
    # what other geoms could we use
    # geom_ridgeline(fill="lightblue") +
     geom_density_ridges() +
    # geom_density_ridges2 - includes bottom line
    # geom_density_ridges(rel_min_height = 0.01) - shortens tails
    # geom_density_ridges_gradient
    # geom_halfeyeh(.width = .95) +
    geom_vline(xintercept = 0, color = "grey") +
    labs(y = "Covariates") +
    facet_wrap(~ levels, ncol = 5)
}
